--- 
title: "Correlations background"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(
    c(.packages(), 'bookdown', 'knitr', 'rmarkdown')
  , 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Copulas

## Quick copula refresher

What's a copula? It's a multivariate distribution, with support on $\Re^N$.

```{r}
library(copula)
library(gridExtra)
library(tidyverse)
```

## Fitting a copula

```{r}
mat_obs <- tbl_fx %>% 
  select(date, currency, rate_change) %>% 
  filter(!is.na(rate_change)) %>% 
  tidyr::spread(currency, rate_change) %>% 
  select(-date) %>% 
  as.matrix()

mat_pseudo <- mat_obs %>% 
  copula::pobs()
```


```{r }
plt_obs <- mat_obs %>% 
  as.data.frame() %>% 
  ggplot(aes(CAD, EUR)) + 
  geom_point()

plt_pseudo <- mat_pseudo %>% 
  as.data.frame() %>% 
  ggplot(aes(CAD, EUR)) + 
  geom_point()

grid.arrange(plt_obs, plt_pseudo, nrow = 1)
```

```{r}
fit_fx <- fitCopula(
    gumbelCopula(dim = 3)
  , data = mat_pseudo
  , method = 'ml'
)

fit_fx
confint(fit_fx)
```

```{r}
library(CASdatasets)
data("lossalae")
```

```{r }
lossalae %>% 
  ggplot(aes(Loss, ALAE)) + 
  geom_point() + 
  scale_x_log10() + 
  scale_y_log10()
```

## Multivariate Copulas for Financial Modeling [@MultivariateCopulas]

## Dependence Models and the Portfolio Effect [@DependenceModels]

## Quantifying Correlated Reinsurance Exposures with Copulas [@QuantifyingCorrelatedReinsurance]

## Tails of copulas [@]

Here, Venter [@] talks through some issues about dependence in the tail of the copula.

Venter introduces measurements for right and left tail concentration:

$$R(z) = Pr(U > z | V > z)$$

## Multivariate Copulas for Financial Modeling

This paper [@Multivar80:online] looks at the issues associated with copulas higher than bivariate. 

We learn about a few new copulas: the IT, and the Joe.

As an example, the authors fit several copulas to currency exchange data.



<!--chapter:end:Copulas.Rmd-->

# Example data

```{r}
library(tidyverse)
library(quantmod)
```


```{r }
get_fx_tibble <- function(which_fx) {

  obj_xts <- getFX(which_fx, auto.assign = FALSE) %>% 
    as.data.frame() %>% 
    as_tibble(rownames = 'date')
  
}

tbl_fx <- map_dfc(
    c('USD/GBP', 'USD/EUR', 'USD/CAD'), get_fx_tibble
  ) %>% 
  select(-date1, -date2) %>% 
  mutate(date = as.Date(date)) %>% 
  select_all(gsub, pattern = 'USD.', replacement = '') %>% 
  tidyr::gather(currency, rate, -date) %>% 
  group_by(currency) %>% 
  arrange(date) %>% 
  mutate(
      rate_change = rate / dplyr::lag(rate) - 1
    , normalized_rate = rate / first(rate)
  ) %>% 
  ungroup()
```

```{r}
tbl_fx %>% 
  ggplot(aes(date, rate, color = currency)) + 
  geom_line()
```

```{r}
tbl_fx %>% 
  ggplot(aes(date, normalized_rate, color = currency)) + 
  geom_line()
```

```{r}
tbl_fx %>% 
  ggplot(aes(date, rate_change, color = currency)) + 
  geom_line()
```

```{r}
tbl_fx %>% 
  select(-rate_change) %>% 
  tidyr::spread(currency, rate) %>% 
  ggplot(aes(CAD, GBP)) +
  geom_point()
```

A visual inspection of the plot suggests that _changes_ in FX are not as strongly correlated.

```{r}
tbl_fx %>% 
  select(-rate) %>% 
  tidyr::spread(currency, rate_change) %>% 
  ggplot(aes(CAD, GBP)) +
  geom_point()
```


<!--chapter:end:example_data.Rmd-->

# Meyers

```{r}
library(tidyverse)
```

## PPT - "Risk and Return - Part 1Introduction to VaR and RAROC"

co-written with Freestone and Nakada

Slide 12

"CorrelationMultiple Line Parameter Uncertainty 

Select $\beta$  from a distribution with E[$\beta$] = 1 and Var[$\beta$] = b.
For each line h, multiply each loss by $\beta$.
Generates correlation between lines.
"

```{r}
lines <- c("WC", "GL")
```

```{r}
beta_prob <- c(1/6, 2/3, 1/6)
form_betas <- function(b) {
  c(
      1 - sqrt(3 * b)
    , 1
    , 1 + sqrt(3 * b)
  )
}

sum(beta_prob * form_betas(0))

sample(form_betas(0.03), size = 1, prob = beta_prob)

rbeta_param <- function(n, b){
  sample(form_betas(0.03), size = n, prob = beta_prob, replace = TRUE)
}
```

```{r}
sims <- 1e3
tbl_loss <- tibble(
    gl_loss = rlnorm(sims, log(10e3))
  , wc_loss = rgamma(sims, shape = 2)
  , beta = sample(form_betas(0.1), size = sims, replace = TRUE, prob = beta_prob)
  , gl_loss_adj = gl_loss * beta
  , wc_loss_adj = wc_loss * beta
)
```

```{r}
tbl_loss %>% 
  ggplot() +
  geom_point(aes(gl_loss, wc_loss), color = 'blue', alpha = 0.5) +
  geom_point(aes(gl_loss_adj, wc_loss_adj), color = 'red', alpha = 0.5) +
  scale_x_log10() + 
  scale_y_log10() +
  NULL
```

Hmm, I'm not convinced. I must be doing something wrong. Let's create a function to construct the tibble and then let's plot only the correlated amounts. 

```{r}
make_loss <- function(b, ln_loss = 10e3, shape = 2) {
  tibble(
    gl_loss = rnorm(sims)
  , wc_loss = rnorm(sims)
  , beta = sample(form_betas(b), size = sims, replace = TRUE, prob = beta_prob)
  , gl_loss_adj = gl_loss * beta
  , wc_loss_adj = wc_loss * beta
  , b = b)
}
  #   gl_loss = rlnorm(sims, log(ln_loss))
  # , wc_loss = rgamma(sims, shape = shape)
```

```{r}
tbl_loss <- map_dfr(c(0, .03, .05, .1, 0.2, 0.5, 1, 2), make_loss)
```

```{r }
tbl_loss %>%
  ggplot(aes(gl_loss_adj, wc_loss_adj)) +
  geom_point() +
  facet_wrap(~b, scales = 'free')
```

Further questions:

1. Where do we get our common shock model?
2. How do we parameterize it?

## The Aggregation and Correlation of Insurance Exposure

co-written with Klinker and Lalonde

Page 19, simulation algorithm #2 uses a similar technique. There is a random $\beta$ with $E[\beta] = 1$ and $Var[\beta] = b$. Note, though, that $\beta$ is applied after the losses for each line have been correlated.

The presentation suggested that each pair of losses had the same $\beta$, but that $\beta$ could vary from one pair to the next (see slide 15). Pages 19-20 of the paper suggest that there is one $\beta$ applied to two sets of variables $X_1$ and $X_2$. Let's try that.

```{r}
sims <- 100
tbl_loss <- tibble(
    x_1 = rnorm(sims, sd = 0.2)
  , x_2 = rnorm(sims, sd = 0.2)
  , beta = rbeta_param(sims, 2)
)

samp_beta <- rbeta_param(1, 2)
tbl_loss %>%
  ggplot(aes(x_1 * samp_beta, x_2 * samp_beta)) +
  geom_point()
```

Or does it suggest that? I've randomly done 10 or 12 plots and they look nothing like what's in the paper. Jesus christ. 

Anyway. Notes/questions:

1. What restrictions do we have on the distribution for $\beta$?
2. The imputed correlation is sensitive to the variability in the underlying variables. Does this mean that observed correlation is masked when highly skewed distribution are in play? I would almost think the opposite. Cat losses, financial crisis: highly skewed experience, but correlation is evident when large losses occur.
3. The authors use separate shocks for frequency and severity. Has much work been done on this point?

## Meyers response to Wang

Meyers has it that Wang spends a fair bit of time on correlation caused by parameter uncertainty.

<!--chapter:end:meyers.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:references.Rmd-->

# Wang

<!--chapter:end:Wang.Rmd-->

