# Copula refresher

What's a copula? It's a multivariate distribution, with support on $\Re^N$. We use them to simulate multivariate losses which need not be independent and identically distributed.

## Support in R packages

Comes primarily from the `copula` package though there are some others. 

```{r include = FALSE}
library(gridExtra)
library(tidyverse)
```

```{r}
library(copula)
```

## Visualize multivariate data

### Simulations

### Actual data

Load in our sample FX data.

```{r}
load(
  file = file.path('data', 'fx.rda')
)
```

```{r}
mat_obs <- tbl_fx %>% 
  select(date, currency, rate_change) %>% 
  filter(!is.na(rate_change)) %>% 
  tidyr::spread(currency, rate_change) %>% 
  select(-date) %>% 
  as.matrix()

mat_pseudo <- mat_obs %>% 
  copula::pobs()
```


```{r }
plt_obs <- mat_obs %>% 
  as.data.frame() %>% 
  ggplot(aes(CAD, EUR)) + 
  geom_point()

plt_pseudo <- mat_pseudo %>% 
  as.data.frame() %>% 
  ggplot(aes(CAD, EUR)) + 
  geom_point()

grid.arrange(plt_obs, plt_pseudo, nrow = 1)
```

## Fitting a copula

[@Charpentier] references four methods for fitting a copula. The example below will use maximum likelihood.

```{r}
fit_fx <- fitCopula(
    gumbelCopula(dim = 3)
  , data = mat_pseudo
  , method = 'ml'
)

fit_fx
confint(fit_fx)
```

Another example from [@Charpentier] using loss and ALAE data.

```{r}
library(CASdatasets)
data("lossalae")
```

```{r }
lossalae %>% 
  ggplot(aes(Loss, ALAE)) + 
  geom_point() + 
  scale_x_log10() + 
  scale_y_log10()
```

